The Opioid Crisis: State Regulations and Labor Market Outcomes \\ [2ex] \large CEMFI

### 2024-06-12 slides/introduction.tex
paper ongoing

    \begin{wideitemize}
        \item Policies aimed at stoping opioid misuse
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] Increased participation rates only where \(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{was not binding}
            \item[\textcolor{fblu}{\textbullet}] The increase was short-lived, but the impact on unemployment rates was persistent
            \item[\textcolor{fblu}{\textbullet}] Their impact on prescription rates seem to be the main, but not the only, driver of these results
        \end{wideitemize}
        \item At the same time
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] They had no labor market consequences where \(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{was binding}
            \item[\textcolor{fblu}{\textbullet}] Their impact on heroin and synthetic opioid deaths was increasing in \(\textcolor{fblu}{w^{min}}\) bindingness 
        \end{wideitemize}
    \end{wideitemize}

>>>>

    \begin{wideitemize}
        \item Policies aimed at stopping opioid misuse
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] Increased participation rates only where \(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{was not binding}
            \item[\textcolor{fblu}{\textbullet}] The increase was short-lived, but the impact on unemployment rates was persistent
            \item[\textcolor{fblu}{\textbullet}] Their impact on prescription rates seem to be the main, but not the only, driver of these results
        \end{wideitemize}
        \item At the same time
        \vspace{9pt}
        \begin{wideitemize}
            \item[\textcolor{fblu}{\textbullet}] They had no labor market consequences where \(\textcolor{fblu}{w^{min}}\) \textcolor{fblu}{was binding}
            \item[\textcolor{fblu}{\textbullet}] Their impact on heroin deaths was increasing in \(\textcolor{fblu}{w^{min}}\) bindingness 
        \end{wideitemize}
    \end{wideitemize}
